Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-10 demystify.tex
updates

While I cannot speak for others, I do not check your statements for AI contents. First, I do not have the time to do that.  It is much easier for me to just read the statement and see if it makes sense and stands out (\autoref{sec:ievaluate}). Hint: AI-generated content reads very strangely and faculty is just too experienced in reading essays and SOPs from students
to not notice it.
Second, AI-checking technology is very unreliable and inconsistent (e.g., a checker might claim that 80\% of an essay is AI-generated while another says it is 0\%).  Third, while it is not OK to use AI to write your statement (as it is both easy to detect and just feels wrong), I think it is fine to use it to help you polish your writing, e.g., I find the ``proofread'' feature in Apple's \texttt{Writing Tools} useful to fix writing mistakes.

>>>>

While I cannot speak for others, I do not check your statements for AI contents. First, I do not have the time to do that.  It is much easier for me to just read the statement and see if it makes sense and stands out (\autoref{sec:ievaluate}). Hint: AI-generated content reads very strangely and faculty is just too experienced in reading essays and SOPs from students
to not notice it.
Second, AI-checking technology is very unreliable and inconsistent (e.g., a checker might claim that 80\% of an essay is AI-generated while another says it is 0\%).  Third, while it is not OK to use AI to write your statement (as it is both easy to detect and just feels wrong), I think it is fine to use it to help you polish your writing, e.g., the ``proofread'' feature in Apple's \texttt{Writing Tools} is quite useful for fixing writing issues.
